**Results Template**

### 2021-09-16 scripts/claudia/data processing.Rmd
deception task
data combined to include 80 trials, trial number, condition, inclusion

@@

mydata <- mydata %>% 
  rename(Name = Q2,
         ID = Q3,
         Matric = Q4,
         HP = Q5,
         Email = Q6,
         Gender = Q7,
         Age = Q8,
         Birthday = Q9,
         handedness = Q10,
         School = Q11,
         Course = Q12,
         Polyjc = Q13,
         Ethnicity = Q14,
         Religion = Q15,
         Nationality = Q16,
         RaisedinSG = Q17,
         LivedinSG = Q18) %>% 
  mutate(ID = as.numeric(ID)) %>% 
  arrange(ID)

@@

data <- mydata %>% 
  rename(response = mouse_2.clicked_name,
         responsetime = mouse_2.time) %>% 
  mutate(answer = ifelse(correct == response, 1, 0))

results <- data %>%
  group_by(participant, condition) %>%
  summarise(total = sum(answer)) %>%
  pivot_wider(names_from = condition, values_from = total) %>%
  mutate(yoni_total = affect+cognitive+physical) %>%
  rename(yoni_affective = affect,
         yoni_cognitive = cognitive,
         yoni_physical = physical,
         ID = participant)

@@

  mutate(hbcount_reported = str_remove_all(hbcount_reported, "Enter Number")) %>% 
  mutate(hbcount_reported = as.numeric(hbcount_reported)) %>% 
  mutate(HCT_confidence = str_replace_all(HCT_confidence, "None", "0")) %>% 
  mutate(HCT_confidenceRT = str_replace_all(HCT_confidenceRT, "None", "0")) %>% 
  mutate(HCT_confidence = as.numeric(HCT_confidence)) %>%

@@

```{r deception}

```

```{r merge all}
data_combined <- read.csv("demo.csv") %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q")))

>>>>

```{r clear everything}
rm(list=ls())
cat("\014")
```

@@

mydata <- mydata %>% 
  rename(Name = Q2,
         ID = Q3,
         Matric = Q4,
         HP = Q5,
         Email = Q6,
         Gender = Q7,
         Age = Q8,
         Birthday = Q9,
         Handedness = Q10,
         School = Q11,
         Course = Q12,
         Polyjc = Q13,
         Ethnicity = Q14,
         Religion = Q15,
         Nationality = Q16,
         RaisedinSG = Q17,
         LivedinSG = Q18) %>% 
  mutate(ID = as.numeric(ID)) %>% 
  arrange(ID)

@@

data <- mydata %>% 
  rename(response = mouse_2.clicked_name,
         responseRT = mouse_2.time,
         ID = participant) %>% 
  mutate(answer = ifelse(correct == response, 1, 0)) %>% 
  select(ID, everything()) #move ID column to front

results <- data %>%
  group_by(ID, condition) %>%
  summarise(total = sum(answer)) %>%
  pivot_wider(names_from = condition, values_from = total) %>%
  mutate(yoni_total = affect+cognitive+physical) %>%
  rename(yoni_affective = affect,
         yoni_cognitive = cognitive,
         yoni_physical = physical)

@@

  mutate(hbcount_reported = str_remove_all(hbcount_reported, "Enter Number")) %>% 
  mutate(hbcount_reported = as.numeric(hbcount_reported)) %>% 
  mutate(HCT_confidence = as.numeric(HCT_confidence)) %>%

@@

```{r deception subj}
rm(list=ls())
cat("\014")

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)] %>% 
    mutate(DT_trial = c(1:80)) %>% 
    mutate(DT_condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

inclusion <- read.csv("../final_processing/Errors.csv") %>%
  rename(ID = ï..participant,
         DT_trial = Trial,
         inclusion = Inclusion,
         inclusion2 = Inclusion2)

data <- mydata %>% 
  rename(DT_item = V1,
       DT_style = V2,
       DT_instruction = V3,
       DT_question = V4,
       DT_confidence = V35,
       DT_confidenceRT = V36,
       ID = V47) %>%

  mutate(DT_confidence = as.numeric(DT_confidence)) %>% 
  mutate(DT_confidenceRT = as.numeric(DT_confidenceRT)) %>% 
  mutate(DT_instruction = as.factor(DT_instruction)) %>% 
  mutate(ID = as.numeric(ID)) %>% 
  left_join(inclusion) %>%

  select(ID, DT_trial, DT_condition, inclusion, inclusion2, everything()) #move columns to front

results <- data %>% 
  group_by(ID, DT_instruction, DT_style) %>% 
  summarise(DT_confidence_avg = mean(DT_confidence), DT_confidenceRT_avg = mean(DT_confidenceRT))

write.csv(data, file = "deceptiontask_extracted.csv", row.names=FALSE)
write.csv(results, file = "deceptiontask_processed.csv", row.names=FALSE)
```

```{r combine data}
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))
